# Evaluating Hierarchical Logit and Probit Regression Models on Economic Recessions of 10 Organization for Economic Cooperation and Development (OECD) Countries
## A Bayesian Computing Project by Yin Kwong John Lee, Yuanbin Sun, and Chenyi Yu

**This markdown file contains the portion of code contributed by Yin Kwong John Lee**

<br/><br/>

(Note: Some code chunks may take a long time to run (e.g. NUTS for Random Walk (RW) Logit Regression Model and Random Walk (RW) Probit Regression Model))

```{r,include=FALSE}
# Initializaing work directory 
# <!-- working directory here -->

# Loading libraries
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(grid)
library(dplyr)
library(ggplotify)


```

**Preliminary Visualiization and Exploratory Data Analysis**<br/>
```{r,message=FALSE,warning=FALSE,fig.height=5,fig.width=15}
# Data frame containing recession indicators and outcomes of the 10 OECD countries from October 1999 to September 2019
oecdTable<-read.csv("./data/manipulated_data/oecdTable.csv",stringsAsFactors = FALSE)
library(lubridate)
# Formatting dates to %Y%m%d
oecdTable$Date=mdy(oecdTable$Date)
# Visualize the durations of recession for each OECD country
recPlot<-ggplot(oecdTable,aes(x=Date,y=recBinary,color=Country))+geom_bar(stat="identity")+facet_wrap(~Country,nrow=5)+labs(title="Recession Time Series of the 10 OECD Countries",x="Time",y="Recession Outcome",caption="Figure 1 Recession time series of the 10 OECD countries from 1999-2019.")+theme(plot.caption=element_text(hjust=0,size=10,face="italic"))
recPlot
#---------------------------------------------------------
# For each year, calculate the proportion of time that a recession occurs
recDuration<-c()
for (i in 1:200){
  recDuration[i]<-mean(oecdTable$recBinary[seq(1,2412,12)[i]:(seq(1,2412,12)[i+1]-1)])
}
# Giving year labels
recYear<-c()
for (yr in 2000:2019){
  recYear<-append(recYear,paste0("yr",toString(yr)))
}
# Store result in a data frame
oecdYearlyRecDuration<-data.frame(Country=c("USA","UK","NET","LUX","JAP","KOR","GER","FRA","DEN","CAN"), matrix(recDuration,nrow=10,ncol=20,byrow=TRUE));colnames(oecdYearlyRecDuration)=c("Country",recYear)
# Example plots to show linearity and non-linearity
linRecDuration<-ggplot(oecdYearlyRecDuration)+geom_point(aes(x=yr2014,y=yr2009,label=Country))+xlim(0,1)+ylim(0,1)+geom_text_repel(aes(x=yr2014,y=yr2009,label=Country),nudge_x=0.05,size=3)+xlab("Recesscion by country (2014)")+ylab("Recession by country (2009)")
nonlinRecDuration<-ggplot(oecdYearlyRecDuration)+geom_point(aes(x=yr2019,y=yr2016,label=Country))+xlim(0,1)+ylim(0,1)+geom_text_repel(aes(x=yr2019,y=yr2016,label=Country),nudge_x=0.05,size=3)+xlab("Recesscion by country (2019)")+ylab("Recession by country (2016)")

grid.arrange(linRecDuration,nonlinRecDuration,nrow=1,ncol=2,bottom=textGrob("Figure 2 (a) Percentage of time throughout the year that recession persisted, in 2009 and 2014. (b)  Percentage of time throughout the year that recession persisted, in 2016 and 2019.",x=0.05,y=0.5,just="left",gp=gpar(fontsize=10,fontface="italic")))

#--------------------------------------------------------------------------
# Representing the countries with numeric group numbers 
oecdTable$Country<-oecdTable$Country%>%sapply(as.factor)%>%sapply(unclass)
# Representing the times with numeric group numbers 
oecdTable$Date<-oecdTable$Date%>%sapply(as.factor)%>%sapply(unclass)
# Standardizing the covariates in matrix form 
x_std<-oecdTable%>%select(-c(Country,Date,recBinary))%>%scale(center=TRUE,scale=TRUE)%>%as.matrix()

#--------------------------------------------------------------------------
# Chi-square tests for independence of outcome between countries
chisq.test(table(oecdTable$Country,oecdTable$recBinary))
# Chi-square tests for independence of outcome throughout time 
chisq.test(table(oecdTable$Date,oecdTable$recBinary))
#---------------------------------------------------------------------------------------
cor.test(oecdTable$Date,oecdTable$retailSales)
cor.test(oecdTable$Date,oecdTable$indProd)
cor.test(oecdTable$Date,oecdTable$unempRate)
cor.test(oecdTable$Date,oecdTable$realPersInc)
cor.test(oecdTable$Date,oecdTable$realGDP)

```


<br/>**Posterior Predictive Checks**<br/>
```{r,message=FALSE,warning=FALSE}
set.seed(1)
# posterior predictive test using the test quantity T = number of switches between 0 and 1 in the actual obeservations
N_switches_obs<-sum(sapply(2:length(oecdTable$recBinary),function(i) oecdTable$recBinary[i]!=oecdTable$recBinary[i-1]))
# number of iterations for drawing from the posterior 
M=10000
# number of response switched for all iterations
N_switches<-rep(NA,M)

for (m in 1:M){
  # sample alpha from posterior 
  alpha=rnorm(1,0,10)
  # sample beta from poosterior
  beta=rnorm(5,0,2.5)
  Xbeta<-x_std%*%beta
  # sample yrep from posterior predictive distribution
  yrep=rbinom(n=length(oecdTable$recBinary),size=1,prob=plogis(alpha+Xbeta))
  N_switches[m] = sum(sapply(2:length(oecdTable$recBinary),function(i) yrep[i]!= yrep[i-1]))
}
# proportion of simulations that have more switches than the actual observation (Bayesian p-value)
pp_pval=mean(N_switches>=N_switches_obs)

# Comparing the number of switchesvia histogram
library(latex2exp)
hist(N_switches, xlab = TeX("$T(recBinary^{rep})$"),main =TeX(paste("$\\hat{p} = $",pp_pval))) 
abline(v = N_switches_obs, col = "red")
legend("topright", legend = "T(recBinary)=96", col = "red", lty = 1, bty = "n")

```


<br/>**Maximum Liklihood Estimation(MLE) under Generalized Linear Model(GLM)**<br/>
<br/>*MLE for Logit Regression Model*<br/>
```{r,message=FALSE,warning=FALSE}
# fitting glm on time-inclusive data for logistic regression
oecdLogitMLE<-glm(recBinary~.,data=data.frame(cbind(oecdTable[c("Date","recBinary")],x_std)),family=binomial("logit"))
# summary of the fit
summary(oecdLogitMLE)

```

<br/>*MLE for Probit Regression Model*<br/>
```{r,message=FALSE,warning=FALSE}
# fitting glm on time-inclusive data for probit regression
oecdProbitMLE<-glm(recBinary~.,data=data.frame(cbind(oecdTable[c("Date","recBinary")],x_std)),family=binomial("probit"))
#summary of the fit 
summary(oecdProbitMLE)

```



<br/>**No-U-Turn Sampling(NUTS) Approach**<br/>
```{r,message=FALSE,warning=FALSE}
library(rstan)
library(bayesplot)
library(rstanarm)
# Configurating stan to use multicore function fromm pc
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

```

<br/>*No-U-Turn Sampling with Weighted-times(WT) Logistic Regression Model*<br/>
```{r}
## see "oecdLogitWT.stan"

# Listing data necessary to fit a WT logistic regression model
oecdLogitData_WT<-list(N=2400,y=array(oecdTable$recBinary),x=as.matrix(cbind(oecdTable[c("Date")],x_std)))
# NUTS sampling from a WT logistic regression model
oecdLogitNUTS_WT<-stan(file="oecdLogitWT.stan",data=oecdLogitData_WT,chains=4,warmup=2000,iter=4000,cores=2,refresh=0)

# error plot
errLogitWT<-plot(oecdLogitNUTS_WT)+ vline_0(size=1.5,color="blue",linetype=2)

```


<br/>*No-U-Turn Sampling with Simple Random Intercept(SRI) Logistic Regression Model*<br/>
```{r,,message=FALSE,warning=FALSE}
## see "oecdLogitSRI.stan"

# Listing data necessary to fit a SRI logistic regression model
oecdLogitData_SRI<-list(N=2400,C=10,K=5,y=array(oecdTable$recBinary),x=x_std,g=array(oecdTable$Date))
# NUTS sampling from a SRI logistic regression model
oecdLogitNUTS_SRI<-stan(file="oecdLogitSRI.stan",data=oecdLogitData_SRI,chains=4,warmup=2000,iter=6000,cores=2,refresh=0)

# extracting stanfit mean 95% CI's for each parameters
alphaLowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[1,1]
alphaMeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[1,1]
alphaUpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[1,2]
wtLowerLogit_SRI<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2:2401,])[[1]]
wtMeanLogit_SRI<-mean(summary(oecdLogitNUTS_SRI)$summary[,"mean"][2:2401])
wtUpperLogit_SRI<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2:2401,])[[2]]
beta1LowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2402,1]
beta1MeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[2402,1]
beta1UpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2402,2]
beta2LowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2403,1]
beta2MeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[2403,1]
beta2UpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2403,2]
beta3LowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2404,1]
beta3MeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[2404,1]
beta3UpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2404,2]
beta4LowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2405,1]
beta4MeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[2405,1]
beta4UpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2405,2]
beta5LowerLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2406,1]
beta5MeanLogit_SRI<-summary(oecdLogitNUTS_SRI)$summary[2406,1]
beta5UpperLogit_SRI<-posterior_interval(as.matrix(oecdLogitNUTS_SRI),prob=0.95)[2406,2]
# storing mean and CI's into a dataframe
errLogitSRI<-data.frame(parameters=c("alpha","w_t","beta[1]","beta[2]","beta[3]","beta[4]","beta[5]"),mean=c(alphaMeanLogit_SRI,wtMeanLogit_SRI,beta1MeanLogit_SRI,beta2MeanLogit_SRI,beta3MeanLogit_SRI,beta4MeanLogit_SRI,beta5MeanLogit_SRI),lower=c(alphaLowerLogit_SRI,wtLowerLogit_SRI,beta1LowerLogit_SRI,beta2LowerLogit_SRI,beta3LowerLogit_SRI,beta4LowerLogit_SRI,beta5LowerLogit_SRI),upper=c(alphaUpperLogit_SRI,wtUpperLogit_SRI,beta1UpperLogit_SRI,beta2UpperLogit_SRI,beta3UpperLogit_SRI,beta4UpperLogit_SRI,beta5UpperLogit_SRI))
# plotting error bars
errLogitSRI<-ggplot()+geom_errorbarh(data=errLogitSRI,aes(y=parameters,x=upper,xmin=upper,xmax=lower),height=0.2,size=2,color="maroon4")+geom_point(data=errLogitSRI,aes(y=parameters,x=mean),size=4,shape=21,fill="black")+theme_bw()+ylab("")+xlab("")+geom_vline(xintercept=0, linetype="dashed",size=1.5,color="blue")


```

<br/>*No-U-Turn Sampling with Random Walk(RW) Logistic Regression Model*<br/>
```{r,message=FALSE,warning=FALSE}
## "oecdLogitRW.stan"

# Listing data necessary to fit a RW logistic regression model
oecdLogitData_RW<-list(N=2400,C=10,T=240,K=5,y=as.array(matrix(oecdTable$recBinary,nrow=10,ncol=240,byrow=TRUE)),x=x_std)
# NUTS sampling from a RW logistic regression model
oecdLogitNUTS_RW<-stan(file="oecdLogitRW.stan",data=oecdLogitData_RW,chains=4,warmup=2000,iter=4000,cores=2,refresh=0)


# extracting stanfit mean 95% CI's for each parameters
alphaLowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[1:240,])[[1]]
alphaMeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[,"mean"][1:240])
alphaUpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[1:240,])[[2]]

beta1LowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+1,240+1200,5),])[[1]]
beta1MeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[241:480,1])
beta1UpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+1,240+1200,5),])[[2]]

beta2LowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+2,240+1200,5),])[[1]]
beta2MeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[481:720,1])
beta2UpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+2,240+1200,5),])[[2]]

beta3LowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+3,240+1200,5),])[[1]]
beta3MeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[721:960,1])
beta3UpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+3,240+1200,5),])[[2]]


beta4LowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+4,240+1200,5),])[[1]]
beta4MeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[961:1200,1])
beta4UpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+4,240+1200,5),])[[2]]


beta5LowerLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+5,240+1200,5),])[[1]]
beta5MeanLogit_RW<-mean(summary(oecdLogitNUTS_RW)$summary[1201:1440,1])
beta5UpperLogit_RW<-colMeans(posterior_interval(as.matrix(oecdLogitNUTS_RW),prob=0.95)[seq(240+5,240+1200,5),])[[2]]


# storing mean and CI's into a dataframe
errLogitRW<-data.frame(parameters=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","beta[5]"),mean=c(alphaMeanLogit_RW,beta1MeanLogit_RW,beta2MeanLogit_RW,beta3MeanLogit_RW,beta4MeanLogit_RW,beta5MeanLogit_RW),lower=c(alphaLowerLogit_RW,beta1LowerLogit_RW,beta2LowerLogit_RW,beta3LowerLogit_RW,beta4LowerLogit_RW,beta5LowerLogit_RW),upper=c(alphaUpperLogit_RW,beta1UpperLogit_RW,beta2UpperLogit_RW,beta3UpperLogit_RW,beta4UpperLogit_RW,beta5UpperLogit_RW))

# plotting error bars
errLogitRW<-ggplot()+geom_errorbarh(data=errLogitRW,aes(y=parameters,x=upper,xmin=upper,xmax=lower),height=0.2,size=2,color="maroon4")+geom_point(data=errLogitRW,aes(y=parameters,x=mean),size=4,shape=21,fill="black")+theme_bw()+ylab("")+xlab("")+geom_vline(xintercept=0, linetype="dashed",size=1.5,color="blue")


```


<br/>*No-U-Turn Sampling with Weighted-times(WT) Probit Regression Model*<br/>
```{r}
## see "oecdProbitWT.stan"

# Listing data necessary to fit a WT probit regression model
oecdProbitData_WT<-list(N=2400,y=array(oecdTable$recBinary),x=as.matrix(cbind(oecdTable[c("Date")],x_std)))
# NUTS sampling from a WT probit regression model
oecdProbitNUTS_WT<-stan(file="oecdProbitWT.stan",data=oecdProbitData_WT,chains=1,warmup=2000,iter=4000,cores=2,refresh=0)

# error plot
errProbitWT<-plot(oecdProbitNUTS_WT)+ vline_0(size=1.5,color="blue",linetype=2)

```

<br/>*No-U-Turn Sampling with Simple Random Intercept(SRI) Probit Regression Model*<br/>
```{r,message=FALSE,warning=FALSE}
## see "oecdProbitSRI"

# Listing data necessary to fit a SRI probit regression model
oecdProbitData_SRI<-list(N=2400,C=10,K=5,y=array(oecdTable$recBinary),x=x_std,g=array(oecdTable$Date))
# NUTS sampling from a SRI probit regression model
oecdProbitNUTS_SRI<-stan(file="oecdProbitSRI.stan",data=oecdProbitData_SRI,chains=4,warmup=2000,iter=6000,cores=2,refresh=0)

# extracting stanfit mean 95% CI's for each parameters
alphaLowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[1,1]
alphaMeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[1,1]
alphaUpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[1,2]
wtLowerProbit_SRI<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2:2401,])[[1]]
wtMeanProbit_SRI<-mean(summary(oecdProbitNUTS_SRI)$summary[,"mean"][2:2401])
wtUpperProbit_SRI<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2:2401,])[[2]]
beta1LowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2402,1]
beta1MeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[2402,1]
beta1UpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2402,2]
beta2LowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2403,1]
beta2MeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[2403,1]
beta2UpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2403,2]
beta3LowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2404,1]
beta3MeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[2404,1]
beta3UpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2404,2]
beta4LowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2405,1]
beta4MeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[2405,1]
beta4UpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2405,2]
beta5LowerProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2406,1]
beta5MeanProbit_SRI<-summary(oecdProbitNUTS_SRI)$summary[2406,1]
beta5UpperProbit_SRI<-posterior_interval(as.matrix(oecdProbitNUTS_SRI),prob=0.95)[2406,2]
# storing mean and CI's into a dataframe
errProbitWT<-data.frame(parameters=c("alpha","w_t","beta[1]","beta[2]","beta[3]","beta[4]","beta[5]"),mean=c(alphaMeanProbit_SRI,wtMeanProbit_SRI,beta1MeanProbit_SRI,beta2MeanProbit_SRI,beta3MeanProbit_SRI,beta4MeanProbit_SRI,beta5MeanProbit_SRI),lower=c(alphaLowerProbit_SRI,wtLowerProbit_SRI,beta1LowerProbit_SRI,beta2LowerProbit_SRI,beta3LowerProbit_SRI,beta4LowerProbit_SRI,beta5LowerProbit_SRI),upper=c(alphaUpperProbit_SRI,wtUpperProbit_SRI,beta1UpperProbit_SRI,beta2UpperProbit_SRI,beta3UpperProbit_SRI,beta4UpperProbit_SRI,beta5UpperProbit_SRI))
# plotting error bars
errProbitSRI<-ggplot()+geom_errorbarh(data=errProbitWT,aes(y=parameters,x=upper,xmin=upper,xmax=lower),height=0.2,size=2,color="maroon4")+geom_point(data=errProbitWT,aes(y=parameters,x=mean),size=4,shape=21,fill="black")+theme_bw()+ylab("")+xlab("")+geom_vline(xintercept=0,linetype="dashed",size=1.5,color="blue")

```
<br/>*No-U-Turn Sampling with Random Walk(RW) Probit Regression Model*<br/>
```{r,message=FALSE,warning=FALSE}
## see "oecdProbitRW"

# Listing data necessary to fit a RW probit regression model
oecdProbitData_RW<-list(N=2400,C=10,T=240,K=5,y=as.array(matrix(oecdTable$recBinary,nrow=10,ncol=240,byrow=TRUE)),x=x_std)
# NUTS sampling from a RW probit regression model
oecdProbitNUTS_RW<-stan(file="oecdProbitRW.stan",data=oecdProbitData_RW,chains=4,warmup=2000,iter=4000,cores=2,refresh=0)


# extracting stanfit mean 95% CI's for each parameters
alphaLowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[1:240,])[[1]]
alphaMeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[,"mean"][1:240])
alphaUpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[1:240,])[[2]]

beta1LowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+1,240+1200,5),])[[1]]
beta1MeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[241:480,1])
beta1UpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+1,240+1200,5),])[[2]]

beta2LowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+2,240+1200,5),])[[1]]
beta2MeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[481:720,1])
beta2UpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+2,240+1200,5),])[[2]]

beta3LowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+3,240+1200,5),])[[1]]
beta3MeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[721:960,1])
beta3UpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+3,240+1200,5),])[[2]]


beta4LowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+4,240+1200,5),])[[1]]
beta4MeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[961:1200,1])
beta4UpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+4,240+1200,5),])[[2]]


beta5LowerProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+5,240+1200,5),])[[1]]
beta5MeanProbit_RW<-mean(summary(oecdProbitNUTS_RW)$summary[1201:1440,1])
beta5UpperProbit_RW<-colMeans(posterior_interval(as.matrix(oecdProbitNUTS_RW),prob=0.95)[seq(240+5,240+1200,5),])[[2]]


# storing mean and CI's into a dataframe
errProbitRW<-data.frame(parameters=c("alpha","beta[1]","beta[2]","beta[3]","beta[4]","beta[5]"),mean=c(alphaMeanLogit_RW,beta1MeanProbit_RW,beta2MeanProbit_RW,beta3MeanProbit_RW,beta4MeanProbit_RW,beta5MeanProbit_RW),lower=c(alphaLowerProbit_RW,beta1LowerProbit_RW,beta2LowerProbit_RW,beta3LowerProbit_RW,beta4LowerProbit_RW,beta5LowerProbit_RW),upper=c(alphaUpperProbit_RW,beta1UpperProbit_RW,beta2UpperProbit_RW,beta3UpperProbit_RW,beta4UpperProbit_RW,beta5UpperProbit_RW))

# plotting error bars
errProbitRW<-ggplot()+geom_errorbarh(data=errProbitRW,aes(y=parameters,x=upper,xmin=upper,xmax=lower),height=0.2,size=2,color="maroon4")+geom_point(data=errProbitRW,aes(y=parameters,x=mean),size=4,shape=21,fill="black")+theme_bw()+ylab("")+xlab("")+geom_vline(xintercept=0, linetype="dashed",size=1.5,color="blue")

```
<br/>Error Plot Summary<br/>
```{r}

grid.arrange(errLogitWT,errLogitSRI,errLogitRW,errProbitWT,errProbitSRI,errProbitRW,nrow=2,ncol=3)
  

```

<br/>**Model Selection**<br/>
```{r}
# Logit_RW
print(oecdLogitNUTS_RW, c('alpha', 'beta'),  probs = c(0.025, 0.975))
oecdLogit_WT <- extract(oecdLogitNUTS_WT,permuted = TRUE)
oecdLogit_SRI <- extract(oecdLogitNUTS_SRI,permuted = TRUE)
oecdProbit_RW <- extract(oecdProbitNUTS_RW,permuted = TRUE)
oecdProbit_WT <- extract(oecdProbitNUTS_WT,permuted = TRUE)
oecdProbit_SRI <- extract(oecdProbitNUTS_SRI,permuted = TRUE)


```

```{r}
library(loo)
log_lik_L_SRI= extract_log_lik(oecdLogitNUTS_SRI,merge_chains=TRUE)

#Logit_SRI

#DIC
bayesEstLogitSRI<-summary(oecdLogitNUTS_SRI)$summary[8:2407,"mean"]
p_DICLogitSRI = 2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - mean(rowSums(log_lik_L_SRI)))
DICLogitSRI = -2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - p_DICLogitSRI)
DICLogitSRI
#WAIC
waic_L_SRI_res = waic(log_lik_L_SRI)
waic_L_SRI = waic_L_SRI_res$estimates["waic","Estimate"]
waic_L_SRI
#LOO_CV
log_lik_L_SRI= extract_log_lik(oecdLogitNUTS_SRI,merge_chains=FALSE)
loo_L_SRI_res = loo(log_lik_L_SRI, r_eff = relative_eff(exp(log_lik_L_SRI)))
loo_L_SRI = loo_L_SRI_res$estimates["looic","Estimate"]
loo_L_SRI
```

```{r}
#Logit_WT
log_lik_L_WT= extract_log_lik(oecdLogitNUTS_WT,merge_chains=TRUE)
#DIC
bayesEstLogitWT<-summary(oecdLogitNUTS_WT)$summary[8:2407,"mean"]
p_DICLogitWT = 2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - mean(rowSums(log_lik_L_WT)))
DICLogitWT = -2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - p_DICLogitWT)
DICLogitWT
#WAIC
waic_L_WT_res = waic(log_lik_L_WT)
waic_L_WT = waic_L_WT_res$estimates["waic","Estimate"]
waic_L_WT
#LOO_CV
log_lik_L_WT= extract_log_lik(oecdLogitNUTS_WT,merge_chains=FALSE)
loo_L_WT_res = loo(log_lik_L_WT, r_eff = relative_eff(exp(log_lik_L_WT)))
loo_L_WT = loo_L_WT_res$estimates["looic","Estimate"]
loo_L_WT

```
```{r}
library(loo)
log_lik_P_SRI= extract_log_lik(oecdProbitNUTS_SRI,merge_chains=TRUE)

#Probit_SRI
#DIC
bayesEstProbitSRI<-summary(oecdProbitNUTS_SRI)$summary[8:2407,"mean"]
p_DICProbitSRI = 2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - mean(rowSums(log_lik_P_SRI)))
DICProbitSRI = -2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - p_DICProbitSRI)
DICProbitSRI 
#WAIC
waic_P_SRI_res = waic(log_lik_P_SRI)
waic_P_SRI = waic_P_SRI_res$estimates["waic","Estimate"]
waic_P_SRI
#LOO_CV
log_lik_P_SRI= extract_log_lik(oecdProbitNUTS_SRI,merge_chains=FALSE)
loo_P_SRI_res = loo(log_lik_P_SRI, r_eff = relative_eff(exp(log_lik_P_SRI)))
loo_P_SRI = loo_P_SRI_res$estimates["looic","Estimate"]
loo_P_SRI
```

```{r}
#Probit_WT
log_lik_P_WT= extract_log_lik(oecdProbitNUTS_WT,merge_chains=TRUE)

#DIC
bayesEstProbitWT<-summary(oecdProbitNUTS_WT)$summary[8:2407,"mean"]
p_DICProbitWT = 2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - mean(rowSums(log_lik_P_WT)))
DICProbitWT = -2 * (sum(dbinom(x=oecdTable$recBinary,size=1,prob=plogis(alpha+Xbeta),log=TRUE)) - p_DICProbitWT)
DICProbitWT

#WAIC
waic_P_WT_res = waic(log_lik_P_WT)
waic_P_WT = waic_P_WT_res$estimates["waic","Estimate"]
waic_P_WT
#LOO_CV
log_lik_P_WT= extract_log_lik(oecdProbitNUTS_WT,merge_chains=FALSE)
loo_P_WT_res = loo(log_lik_P_WT, r_eff = relative_eff(exp(log_lik_P_WT)))
loo_P_WT = loo_P_WT_res$estimates["looic","Estimate"]
loo_P_WT

```

```{r}
#Model Selection Summary
res_df = data.frame(Logit_WT = c(DICLogitWT,waic_L_WT,loo_L_WT),
                    Probit_WT = c(DICProbitWT,waic_P_WT,loo_P_WT),
                    Logit_SRI = c(DICLogitSRI,waic_L_SRI,loo_L_SRI),
                    Probit_SRI = c(DICProbitSRI,waic_P_SRI,loo_P_SRI))
rownames(res_df) = c("DIC","WAIC","LOO-CV")
res_df
```

<br/>**References**<br/>
(1) https://jrnold.github.io/bugs-examples-in-stan/corporatism.html <br/>
(2) https://data.princeton.edu/pop510/hospStan <br/>





